Jack Antonoff-ification of pop music

### 2023-04-04 outputs/paper/paper.qmd
pushin

\[I blacked out.\]

@@

Antonoff is prolific, to the extent that it is starting to bother people. He has produced and co-produced music for Lorde, Taylor Swift, Florence and the Machine, The Chicks, Clairo, The 1975, Grimes, Zayn, Pink, Lana Del Rey, Olivia Rodrigo, the Minions: The Rise of Gru Soundtrack, and more. All of this and his own bands too (Bleachers, and fun.). When I was getting brunch with a friend one Sunday and a Swift song came on, and she said "Jack Antonoff's gonna kill us all", we both laughed. What my friend was referring to, of course, is the fact that Jack Antonoff seems to be everywhere these days. As Andrew Marantz writes in the New Yorker: "When his band releases an album, the world responds politely. When he produces one by Lorde or Lana Del Rey or Taylor Swift, the world wobbles on its axis".

@@

\[\[He ended up saying a lot of interesting things, which i will transcribe and somehow make use of in this paper later\]

@@

>>>>

\[I glitched.\]

@@

Antonoff is prolific, to the extent that it is starting to bother people. He has produced and co-produced music for Lorde, Taylor Swift, Florence and the Machine, The Chicks, Clairo, The 1975, Grimes, Zayn, Pink, Lana Del Rey, Olivia Rodrigo, the Minions: The Rise of Gru Soundtrack, and more. All of this and his own bands too (Bleachers, and fun.). When I was getting brunch with a friend one Sunday and a Swift song came on, and she said "Jack Antonoff's gonna kill us all", we both laughed. What my friend was referring to, of course, is the fact that Jack Antonoff and his sound seems to be everywhere these days. As Andrew Marantz writes in the New Yorker: "When his band releases an album, the world responds politely. When he produces one by Lorde or Lana Del Rey or Taylor Swift, the world wobbles on its axis".

@@

\[\[He ended up saying a lot of interesting things, which i will transcribe and somehow make use of in this paper later\]\]

@@

My model is driving me bananas.
